candidate genes

### 2019-11-30 analysis/10_specificgenes.Rmd
confirming correlations between hormone and gene expression
new prolactin plots

head(vsd.hyp[1:2])
head(colData.hyp[1:2,])
rownames(colData.hyp) == colnames(vsd.hyp)

@@

```{r PRL}
geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)
head(geneinfo)
```

```{r PRLboxplots, fig.width =5.5, fig.height= 2}
candidategenes <- c("CISH", "SOCS1", "SOCS2", "SOCS2", "SOCS4", "SOCS5", "SOCS6", 
                    "PRL", "PRLR", "STAT5B", "JAK1")
candidates.hyp <- selectcandidatevsds(candidategenes, vsd.hyp, colData.hyp)
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)
candidates.gon <- selectcandidatevsds(candidategenes, vsd.gon, colData.gon)

@@

e <- plotcanddateexpression(candidates.hyp, NULL, candidates.hyp$PRLR, "PRLR")
f <- plotcanddateexpression(candidates.pit, NULL, candidates.pit$PRLR, "PRLR")
g <- plotcanddateexpression(candidates.gon, NULL, candidates.gon$PRLR, "PRLR")

@@

h <- plotcanddateexpression(candidates.hyp, " ", candidates.hyp$STAT5B, "STAT5B")
i <- plotcanddateexpression(candidates.pit, " ", candidates.pit$STAT5B, "STAT5B")
j <- plotcanddateexpression(candidates.gon, " ", candidates.gon$STAT5B, "STAT5B")

@@

@@

>>>>

@@

```{r geneinfo}
geneinfo <- read_csv("../metadata/00_geneinfo.csv") %>%  dplyr::select(Name, geneid, entrezid) %>% arrange(Name)
head(geneinfo)
```

```{r candidategenes, fig.width =5.5, fig.height= 2}
candidategenes <- c("CISH", "SOCS1", "SOCS2", "SOCS2", "SOCS4", "SOCS5", "SOCS6", 
                    "PRL", "PRLR", "STAT5B", "JAK1")

candidates.hyp <- selectcandidatevsds(candidategenes, vsd.hyp, colData.hyp)
candidates.pit <- selectcandidatevsds(candidategenes, vsd.pit, colData.pit)
candidates.gon <- selectcandidatevsds(candidategenes, vsd.gon, colData.gon)

@@

e <- plotcanddateexpression(candidates.hyp, "hypothalamus", candidates.hyp$PRLR, "PRLR")
f <- plotcanddateexpression(candidates.pit, "pituitary", candidates.pit$PRLR, "PRLR")
g <- plotcanddateexpression(candidates.gon, "gonad", candidates.gon$PRLR, "PRLR")

@@

h <- plotcanddateexpression(candidates.hyp, "hypothalamus", candidates.hyp$STAT5B, "STAT5B")
i <- plotcanddateexpression(candidates.pit, "pituitary", candidates.pit$STAT5B, "STAT5B")
j <- plotcanddateexpression(candidates.gon, "gonad", candidates.gon$STAT5B, "STAT5B")

@@

```{r PRL, fig.width = 6, fig.height= 4}
ggplot(candidates.pit, aes(x = as.numeric(treatment), y = PRL)) + 
        geom_smooth(aes(colour = sex)) +
    geom_boxplot(aes(fill = treatment, alpha = sex)) + 
    scale_alpha_manual(values = c(0.75,1)) +
    mytheme() +
    theme(legend.position = "none") +
    scale_color_manual(values = c("female" = "#969696", "male" = "#525252")) +
    labs(y = "PRL expression", x = NULL) +
    scale_x_continuous(breaks = c(1, 2, 3, 4, 5, 6, 7, 8, 9),
                       labels = c( "control", "bldg", "lay", "inc.d3", 
                                   "inc.d9", "inc.d17", "hatch", "n5", "n9"))
```

@@

```{r PRLdf}
head(candidates.pit)
PRLpit <- candidates.pit %>%
  select(sample,sex,treatment,PRL)
head(PRLpit)
write.csv(PRLpit, "../results/10_PRLpit.csv", row.names = F)
```
